%-------------------------
% Entry-level Cover-letter Template in LaTeX
% Made to go with "Entry-level Resume in laTeX" - here
% Version - v1.0
% Last Edits - October 5, 2021
% Author : Jayesh Sanwal
% Reach out to me on LinkedIn(/in/jsanwal), with any suggestions, ideas, issues, etc.


% --- VARIABLES --- %
% Personal Details
\newcommand{\name}{John Snow}
\newcommand{\currentjob}{Lord Commander}
\newcommand{\email}{john.doe@email.com}
\newcommand{\phone}{(XXX) XXX-XXXX}
\newcommand{\linkedin}{johndoe}
\newcommand{\github}{johndoe}

% Application Specific
\newcommand{\recipient}{Colonel Sanders}
\newcommand{\company}{Kentucky Fried Chicken}
\newcommand{\position}{Director of Defence}



%%%%%%% -----------------------------------------------
%%%%%%%  STARTING HERE, DO NOT TOUCH ANYTHING
%%%%%%% -----------------------------------------------
%%%% Define Document type
\documentclass[11pt,a4]{article}

%%%% Include Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
 \usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage[inline]{enumitem}
\usepackage{ragged2e}
\usepackage{anyfontsize}

%%%% Set Margins
\usepackage[margin=1cm]{geometry}


%%%% Set Page Style
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color, Page Number Color, Footer Text
\definecolor{UI_blue}{RGB}{32, 64, 151}
\definecolor{HF_color}{RGB}{179, 179, 179}
\rfoot{{\color{HF_color} \thepage \ of \ 1, Updated \today}}

%%%% Set Heading Format
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large
}{}{0em}{}[\vspace{-0.7cm} \hrulefill \vspace{-0.2cm}]
%%%%%%% --------------------------------
%%%%%%%  END OF "DO NOT TOUCH" REGION
%%%%%%% --------------------------------



\begin{document}
\begin{center}
    \begin{minipage}[b]{0.24\textwidth}
            \large \phone \\
            \large \href{mailto:\email}{\email}
    \end{minipage}%
    \begin{minipage}[b]{0.5\textwidth}
            \centering
            {\Huge \name} \\ %
            \vspace{0.1cm}
            {\color{UI_blue} \Large{\currentjob}} \\
    \end{minipage}%
    \begin{minipage}[b]{0.24\textwidth}
            \flushright \large
            {\href{https://www.linkedin.com/in/\linkedin}{linkedin.com/in/\linkedin} } \\
            \href{https://https://github.com/\github}{github.com/\github}
    \end{minipage}

\vspace{-0.15cm}
{\color{UI_blue} \hrulefill}
\end{center}

\justify
\setlength{\parindent}{0pt}
\setlength{\parskip}{12pt}
\vspace{0.2cm}
\begin{center}
    {\color{UI_blue} \Large{COVER LETTER}}
\end{center}

Date: \today\\
Dear \recipient{},

I am writing to express my keen interest in the \position{} role at \company{}. Having recently learned about the vacancy, I am excited to submit my application and believe that my extensive leadership experience and unique skill set make me an exceptional candidate for this position.

Throughout my distinguished career as the \currentjob{}, I have consistently demonstrated the ability to drive success and achieve exceptional results. I possess a strong track record of leading teams, implementing innovative strategies, and exceeding performance targets.

One of my greatest strengths is my ability to effectively communicate and collaborate with diverse stakeholders, both within and outside of the organization. This skill has allowed me to successfully build and maintain strong relationships with clients, colleagues, and senior management. I am confident that my excellent interpersonal skills will enable me to seamlessly integrate into the dynamic team at \company{} and contribute to its ongoing success.

Furthermore, my extensive experience in \currentjob{} has equipped me with a deep understanding of industry trends and best practices. I am constantly staying abreast of the latest developments and utilizing this knowledge to drive continuous improvement and innovation in my work. I am confident that my expertise in \currentjob{} will allow me to bring fresh perspectives and contribute valuable insights to the \position{} role at \company{}.

In addition to my technical skills and industry knowledge, I possess a strong sense of adaptability and thrive in fast-paced and challenging environments. I am a quick learner who is always eager to take on new responsibilities and broaden my skill set. I am confident that my ability to adapt to new situations and my passion for continuous learning will enable me to make an immediate and meaningful impact in the \position{} role at \company{}.

I am genuinely excited about the opportunity to join \company{} and contribute to its ongoing success. I am confident that my qualifications, combined with my passion for excellence, make me an ideal fit for the \position{} role. Thank you for considering my application. I look forward to the possibility of discussing how my skills and experiences align with the needs of \company{}.



% ----- SIGNATURE ----- %
\vspace{0.5cm}
\raggedright
Yours Faithfully \\ \name \\ \phone \\ \href{mailto:\email}{\email}

\end{document}